Formalizing Stack Safety as a Security Property

### 2021-07-09 submission3/main.tex
wibbles

\judgmentthree[ Call]
              {\(\codemap ~ (\mach ~ \PCname) = \callmap(S)\)}
%              {\(\components = \sealcon ~ \mach\)}
              {\(\components = \{\component | \sealcon ~ \mach ~ \component\}\)}
              {\(\domMap' = \domMap[\components \mapsto \sealed{|\rts|}][\reg \mapsto S(\reg) ~ | ~ r \in \REGS]\)}
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',(\retcon ~ \mach)::\rts\)}

The remaining rules are the same as in the simple model.

@@

We improve upon \citet{SkorstengaardSTKJFP} in two significant ways:
\begin{enumerate}[label=(\roman*)]
\item Our definition captures the intuition that {\em
  every} caller should be protected from its callees.  By contrast,
  \citet{SkorstengaardSTKJFP} describe a class of ``unreasonable'' code components
  that are not protected, because the are capable of dynamic behavior that can compromise
  their own security. Unreasonable code can be viewed as adversarial, but it is equally
  likely to simply be buggy. One can imagine a function that, when called with the wrong
  inputs, behaves unreasonably, but under most circumstances can be
  considered reasonable. \citet{SkorstengaardSTKJFP} would not consider this a
  {\em reasonable component} as defined in their section 4.3.3, and so
  would not guarantee its protection. In contrast, in our setting, individual
  well-behaved activations of the buggy function would be protected.
  \citet{SkorstengaardSTKJFP} note that they support mutually distrustful
  components, but we go a step further. One can think of our hypothetical
  function as ``self-distrustful'' in that the safety of a well-behaved activation
  is not compromised by another, ill-behaved one.

>>>>

\judgmentthree[ Call]
              {\(\codemap ~ (\mach ~ \PCname) = \callmap(S)\)}
%              {\(\components = \sealcon ~ \mach\)}
              {\(\components = \{\component | \sealcon ~ \mach ~ \component\}\)}
              {\(\domMap' = \domMap[\components \mapsto \sealed{|\rts|}][\reg \mapsto S(\reg) ~ | ~ r \in \REGS]\)}
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',(\retcon ~ \mach)::\rts\)}
\apt{Typesetting problem above}
The remaining rules are the same as in the simple model.

@@

We improve upon \citet{SkorstengaardSTKJFP} in two significant ways:
\begin{enumerate}[label=(\roman*)]
\item Our definition captures the intuition that {\em
  every} caller should be protected from its callees.  By contrast,
  \citet{SkorstengaardSTKJFP} describe a class of ``unreasonable'' code components
  that are not protected, because the are capable of dynamic behavior that can compromise
  their own security. Unreasonable code can be viewed as adversarial, but it is equally
  likely to simply be buggy. One can imagine a function that, when called with the wrong
  inputs, behaves unreasonably, but under most circumstances can be
  considered reasonable. \citet{SkorstengaardSTKJFP} would not consider this a
  {\em reasonable component} (as defined in their section 4.3.3), and so
  would not guarantee its protection. In contrast, in our setting, individual
  well-behaved activations of the buggy function would be protected.
  \citet{SkorstengaardSTKJFP} note that they support mutually distrustful
  components, but we go a step further. One can think of our hypothetical
  function as ``self-distrustful'' in that the safety of a well-behaved activation
  is not compromised by another, ill-behaved activiation of the same function.
